```{r data generation, echo = FALSE, results = "hide"}
#### This is a string variable, or short answer question.  
#### It is a pretty basic Confidence Interval.
#### Future Amy:  Can you put a $ before the data entry?  Can you make multiple correct answers?


### Anyway, this first code chunk is all the code for my Confidence Interval.  

library("scales")
library("dplyr")

### I'm sick of randoming!
set.seed(1234)

## pick an n between 12 and 28
n <- sample(12:28,1)

## pick a true mean and standard deviation
mu <-runif(1, min = 8000, max = 20000)
sigma <- runif(1, min = 1000, max = 4000)

# generate data.  Honestly, this isn't 100% necessary, but it's nice, you know?
expenses <-rnorm(n, mu, sigma) 

## find summary statistics
xbar<-  round(mean(expenses),0)
xbardisplay <- as.character(xbar) ## this isn't necessary
s <- round(sd(expenses),0) 

## Picka  Confidence level, and find t  (3 decimal palces, so they can use a table)
CI <- sample(c(90,95,98,99), size = 1)
t <-qt(p =(100-CI)/200, df = n-1, lower.tail = FALSE) %>% 
  round(3)

## Find our Margin of Error, and the Lower and Upper bounds for the CI
ME <- t*s/sqrt(n) 
LB <- round(xbar-ME,2)
UB <- round(xbar+ME,2)

## This is a distractor number, it doesn't doesn't mean anything
cost <- 100*sample(1:5,1) 
  

```


Question
========


A publication specializing in dental information surveyed `r n` dentists at a cost of  `r dollar(cost)` per dentist concerning their monthly office expenses and found that the mean expenditure was `r dollar(xbar)` with a standard deviation of  `r dollar(s)`.  The distribution was approximately normal.  

Give the `r CI`\% confidence interval for the true mean expenditure.  Round your answers to 2 decimal places.  Put the lower bound in the first box, and the upper bound in the second, and do not use dollar signs.

```{r, echo = FALSE}

## Note:  This is markdown, so I put my comments in an r chunk with echo = false.  Carry on!
```

Solution
========
The true mean is between  `r dollar(LB, accuracy = 0.01)` and `r dollar(UB, accuracy = 0.01)`


Meta-information
============
extype: string 
exsolution: `r as.character(LB)` |`r as.character(UB)`
exname: conf_dentist
