
```{r data generation, echo = FALSE, results = "hide"}
### I pulled some financial functions from a collection I have.
### These are built to mimic the financial calculator that my students buy
### Maybe I'll do something someday, but here it is for now.


library(dplyr)
library(scales)

### interesting:functions
### convert interest rates:
ICONV <- function(j1,m1=1,m2=1){
  i1 <- 0.01*j1/m1
  print(i1)
  j2 <- m2*(1+i1)^(m1/m2)-m2
  print(j2)
  return(j2*100)
}


FV <- function(PY, CY=PY, N, IY, PV=0, PMT = 0, BGN = FALSE){
  ## find the FV of a 5-fingered Annuity
  ### Note:  this only works for positive right now, I need to get the signs correct
  
  
  ##convert the interest rate
  if (PY!=CY){
    IY <- ICONV(j1=IY, m1 = CY, m2 = PY)
  }
  
  ### get periodic rate
  i <- 0.01*IY/PY
  #print(i)
  
  ##if PMT ==0
  FV <- PV*(1+i)^N
  
  if (!BGN){
    FV <- PV*(1+i)^N + PMT* ((1+i)^N-1)/i
  } else {
    FV <- PV*(1+i)^N + PMT*(1+i) ((1+i)^N-1)/i
  }
  
  ###ordinary annuity
  ##  PV*(1+i)^N + PMT* ((1+i)^N-1)/i
  
  ##return(dollar(FV, accuracy = 0.01))
  return(FV)
}


### generate all my cool things
price <- sample(15:25,1)*1000
disp_price <- dollar(price)
  
PV <- price - 3000  

PMT <- round(runif(1,3,8),0)*100+49

IY <- round(runif(1,min=1,max =6),2)

### this is the true answer:
FV_real <- FV(PY=12, N=36, IY = IY, PV = PV, PMT = -PMT) %>% abs()

## I generated some fun fake answers
FV_sign <- FV(PY=12, N=36, IY = IY, PV = PV, PMT = PMT)%>% abs()
FV_price <- FV(PY=12, N=36, IY = IY, PV = price, PMT = -PMT)%>% abs()
FV_price_sign <- FV(PY=12, N=36, IY = IY, PV = price, PMT = PMT)%>% abs()


## single-choice list
## Important:  you need to use this function to create the list of possibilities
sc <- num_to_schoice(FV_real, wrong = c(FV_sign, FV_price, FV_price_sign), delta = 2, digits =2)





```


Question
==============
You decide to lease a new  automobile.  The vehicle costs `r dollar(price)` new and you are required to pay all taxes and a \$3,000 downpayment at the beginning of the lease.  The lease payments are `r dollar(PMT)` per month for three years and you know the lease company charges interest at `r IY`\% compounded monthly.

What is the residual value of the car after three years?




```{r questionlist, echo = FALSE, results = "asis"}

## here are my possible answers

answerlist(paste0("$",sc$questions), markup = "markdown")


```




Solution
========

| P/Y C/Y | N | I/Y | PV | PMT | FV | BGN|
|:---:|:------:|:------:|:-------:|:---------:|:---------------:|:-----:|
|$12$|$36$ | $`r as.character(IY)`$ | $`r as.character(PV)`$ | -$`r as.character(PMT)`$ | CPT | OFF|




```{r solutionlist, echo = FALSE, results = "asis"}
#answerlist(ifelse(sc$solutions, "True", "False"), markup = "markdown")
dollar(FV_real, accuracy = 0.01)



```

Meta-information
================
extype: schoice
exsolution: `r mchoice2string(sc$solutions)`
exname: MC_residual_value
exshuffle: 4